%-------------------------
% Resume in Latex
% Author : Praveen Raj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=black,
  citecolor=black
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNH}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListStartBullets}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\usepackage{array}
\makeatletter
\newcommand\HUGE{\@setfontsize\Huge{38}{47}} 
\newcolumntype{L}{>{\hb@xt@\z@\bgroup}l<{\hss\egroup}}
\newcolumntype{C}{>{\centering\arraybackslash}c}
\newcolumntype{R}{>{\hb@xt@\z@\bgroup\hss}r<{\egroup}}
\makeatother

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{L@{\extracolsep{\fill}}C@{\extracolsep{\fill}}R}
  \href{mailto:praveen1220raj@gmail.com}{praveen1220raj@gmail.com} &
  \multirow{2}{*}{
    \begin{tabular}{c}
      \Huge \textbf{Praveen Raj R} 
    \end{tabular}
  } &
  \href{https://praveen-raj.vercel.app}{praveen-raj.vercel.app} \\
  +91 91769 67767 & & Chennai, India
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
\resumeSubheading
  {LCS Controls Private Limited}{Chennai, India}
  {Frontend Engineer}{May 2023 -- Present}

\resumeItemListStart
\resumeItemNH{\textbf{Directed end-to-end frontend development} for production-grade \textbf{B2B} and \textbf{B2C} web applications, delivering scalable user interfaces for industrial monitoring systems and payment analytics platforms.}

\resumeItemNH{\textbf{Built and optimized real-time monitoring dashboards} for Tipper, Checkweigher, and Weighbridge systems, used by \textbf{30+ enterprise clients} to track \textbf{200+ industrial devices}, ensuring stable performance under high-frequency data updates.}

\resumeItemNH{\textbf{Owned development of a customer-facing IoT payment platform, designing scalable state management, API integration layers and reusable UI components} supporting \textbf{20K+ payment events} across \textbf{25+ devices} and \textbf{10+ organizations}.}

\resumeItemNH{\textbf{Designed and implemented a media management module} enabling upload, preview, validation, and management of images and videos, integrated with \textbf{AWS S3} for device-level content delivery.}

\resumeItemNH{\textbf{Developed settlement and reporting workflows}, including calendar-based daily analytics and structured report generation to support accurate business tracking and financial reconciliation.}

\resumeItemNH{\textbf{Architected and delivered a 70+ page corporate website}, improving navigation structure, media loading performance, and SEO metadata management for large-scale product content.}


\resumeItemListEnd

\resumeSubHeadingListEnd
 
 

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
  {AI-Driven Event Organizer Platform (Hostr)}
  {\href{https://github.com/praveen-raj-r/hostr}{GitHub} \;|\;
   \href{https://hostr-ai.vercel.app/}{Live Demo}}
  {Next.js, React, TypeScript, Tailwind CSS, shadcn/ui, Convex, Clerk}
  {}

\resumeItemListStart
  \resumeItemNH{\textbf{AI-assisted event creation workflow} that converts natural-language prompts into structured event data, reducing manual setup complexity.}

  \resumeItemNH{Designed \textbf{real-time event, registration, and ticketing systems} using Convex queries and mutations with instant dashboard updates and no polling.}

  \resumeItemNH{Implemented \textbf{feature gating for different user tiers} using Clerk authentication, middleware-based route protection, and role-based access control.}

  \resumeItemNH{Built the application using \textbf{Next.js App Router} with route-based layouts and optimized rendering for public-facing event pages.}
\resumeItemListEnd

\resumeSubheading
  {AI-Driven Creator Content Platform (Inkbot)}
  {\href{https://github.com/praveen-raj-r/inkbot}{GitHub} \;|\;
   \href{https://inkbotai.vercel.app/}{Live Demo}}
  {Next.js, React, TypeScript, Tailwind CSS, shadcn/ui, Convex, Clerk, ImageKit}
  {}

\resumeItemListStart
  \resumeItemNH{Built an \textbf{AI-assisted content creation workflow} enabling creators to generate, expand, and refine written content through prompt-driven interactions.}

  \resumeItemNH{Engineered \textbf{editor-style and dashboard UI flows} with complex state management to support rich text editing, real-time saving, and responsive user interactions.}

  \resumeItemNH{Implemented a \textbf{social content platform} with user profiles, follow/unfollow flows, likes, comments, and personalized content feeds.}

  \resumeItemNH{Developed a \textbf{creator analytics dashboard} to surface engagement metrics such as views, likes, comments, and follower growth.}

  \resumeItemNH{Integrated \textbf{advanced media handling using ImageKit}, including background removal, smart cropping, aspect ratio control, and optimized image delivery.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Languages}{JavaScript (ES6+), TypeScript, HTML5, CSS3 }
  \resumeSubItem{Frameworks \& Libraries}{React.js, Next.js, Redux, TanStack Query \& Table, React Router, React Hook Form }
  \resumeSubItem{Styling \& UI}{Tailwind CSS, CSS Modules, shadcn/ui, Ant Design}
  \resumeSubItem{Data Visualization}{Recharts, Chart.js}
  \resumeSubItem{Build \& Tooling}{Vite, Webpack, Git, GitHub, REST APIs, Postman, Vercel, AWS S3, Amplify, Netlify }
\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education }
  \resumeSubHeadingListStart
    \resumeSubheading
      {Meenakshi College of Engineering}{Chennai, India}
      {Bachelor of Engineering, Electrical \& Electronics Engineering, \textbf{CGPA: 8.16/10.00}}{Aug 2018 -- May 2022}
   
  \resumeSubHeadingListEnd
 

%-------------------------------------------
\end{document}
